---
title: "Level 4 Analysis QSAR Bake-Off"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= "C:/Users/jwambaug/git/CompTox-ExpoCast-HTTKQSPRs/")
```


First we clear the memory to make sure there are no holdovers from previous R runs
```{r clear_mermor, eval=TRUE}
rm(list=ls()) 
```

To use the code in this vignette, you'll first need to load a few packages (if you haven't already).
```{r load_packages, eval = TRUE}
library(httk)
library(DescTools)
```

Load custom code 
```{r load_code, eval = TRUE}
source("clear_httk.R")
source("tkstats.R")
```




Set the time stamp:
```{r time_stamp, eval = TRUE}
# Time stamp:
output.prefix <- format(Sys.Date(), "%B%Y")
```

```{r load_data, eval= TRUE}
load(file="data/httkinvitro.RData")
load(file="data/Cvt-chems-level1.RData")
load(file="data/operatrainingchems.RData")
load(file="data/Cvt-data.RData")
load(file="data/fittable.RData")
```



We load the TK stats (Level III) at this point because it makes sense to do
the Level II and III calculations are the same time (rather than rewriting 
the parameter values twice).
TK Stats (including Vd and thalf) calculated from CvTdb:

There are chemicals where the in vivo data don't permit empirical fits, drop
those from the level II/III evaluation:
```{r separate_out_badfits, eval=TRUE}
CvT.chems.nofits <- CvT.chems[
  !(CvT.chems$CASRN%in%fittable$CAS) |
  CvT.chems$CASRN %in%subset(fittable,Model=="Flat")$CAS |
  CvT.chems$CASRN %in%subset(fittable,Model=="None")$CAS
  , ]

CvT.data <- subset(CvT.data, !(CAS %in% CvT.chems.nofits$CASRN))
cat(paste(length(unique(CvT.data$DTXSID)),
          "chemicals with good invivoPKfit fits of CvT data.\n"))
cat(paste(dim(subset(fittable,!is.na(Vdist) #| !is.na(V1)
                     ))[1],
          "chemicals where volume of distribution could be estimated (iv data available), allowing us to make empirical predictions.\n"))
```
## Get rid of chemical predictions that are possibly just training set lookups:
```{r remove_training_chems, eval=TRUE}
CvT.chems.notraining <- CvT.chems
for (this.qspr in unique(possible.training.chems$QSPR))
{
  this.subset <- subset(possible.training.chems, QSPR==this.qspr)
  for (this.id in this.subset$DTXSID)
  {
    CvT.chems.notraining[CvT.chems.notraining$DTXSID==this.id,
      paste("Human.Clint",this.qspr,sep=".")]<-NA
    CvT.chems.notraining[CvT.chems.notraining$DTXSID==this.id,
      paste("Human.Fup",this.qspr,sep=".")]<-NA
  }
}
length(unique(CvT.chems.notraining$DTXSID))
```

# Data size
```{r data_Size, eval=TRUE}
CvT.chems.nobad <- CvT.chems[!(CvT.chems %in% CvT.chems.nofits)] 
dim(CvT.data)
length(unique(CvT.data$DTXSID))
length(unique(CvT.chems.nobad$DTXSID))
```

```{r create_consensus_preds, eval=TRUE}
clint.cols <- colnames(CvT.chems.nobad)[
  regexpr("Clint",colnames(CvT.chems.nobad))!=-1]
CvT.chems.nobad$Human.Clint.Max<- signif(apply(
  CvT.chems.nobad[,clint.cols],1,function(x) max(x,na.rm=TRUE)), 4)
CvT.chems.nobad$Human.Clint.Mean<- signif(apply(
  CvT.chems.nobad[,clint.cols],1,function(x) mean(x,na.rm=TRUE)), 4)

for (this.col in c("Human.Clint.Max","Human.Clint.Mean"))
{
  CvT.chems.nobad[is.infinite(CvT.chems.nobad[,this.col]),
                  this.col] <- NA
  CvT.chems.nobad[is.nan(CvT.chems.nobad[,this.col]),
                  this.col] <- NA
}

fup.cols <- colnames(CvT.chems.nobad)[
  regexpr("Fup",colnames(CvT.chems.nobad))!=-1]
CvT.chems.nobad$Human.Fup.Mean <- apply(
  CvT.chems.nobad[,fup.cols],1,function(x) 
    signif(invlogit(mean(sapply(x, function(y) 
      logit(min(max(y,1e-8),(1-1e-8)))),na.rm=TRUE)),4))
```


## Make a version of the prediction matrix where we've replaced QSPR-chemical combinations with no predictions with the consensus predictions:
### Stop doing this -- we will assign mean RMSLE to each QSPR's output, no need to predict with mean predictions
```{r dont_remove_missing_predictions}
CvT.chems.nona <- CvT.chems.nobad
```

```{r initialize_lists}
level2tab.cvt <- 
level2tab.stats <-
level2tab.rmsle <-
level2tab.aafe <- 
level2tab.rmsle.early <-
level2tab.aafe.early <-
level2tab.rmsle.late <-
level2tab.aafe.late <-
level3tab <- list()
```
## Add consensus predictions:
```{r cvt_compare_consensus, eval = TRUE}
this.label <- "HTPBTK-Consensus" 
out <- make_cvt_comparisons(this.label, 
                            "Human.Clint.Max", 
                            "Human.Fup.Mean",
                            CvT.data, 
                            CvT.chems.nona, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab
```



The performance of actual 1 compartment model fits provides an upper limit
of how good we can get (thanks Rusty)
```{r cvt_compare_fits, eval = TRUE}
this.label <- "In Vivo Fits"
fit.chems <- subset(fittable, !is.na(Vdist) #| !is.na(V1)
                    )$DTXSID
out <- makeCvTpredsfromfits(
  subset(CvT.data, DTXSID %in% fit.chems),
  subset(fittable, DTXSID %in% fit.chems),
  label = this.label)

level2tab.cvt[[this.label]] <- out$cvt
level2tab.stats[[this.label]] <- out$stats
level2tab.rmsle[[this.label]] <- out$rmsle
level2tab.aafe[[this.label]] <- out$aafe
level2tab.rmsle.early[[this.label]] <- out$rmsle.early
level2tab.aafe.early[[this.label]] <- out$aafe.early
level2tab.rmsle.late[[this.label]] <- out$rmsle.late
level2tab.aafe.late[[this.label]] <- out$aafe.late
level3tab[[this.label]] <- out$level3tab
```



## Level Four Analysis, an introduction

We finally now want to see how changing particular values for `fittable` to
the consensus predicted values changes the values. 
Another aspect of this is testing the sensitivity of certain values changing,
and describing any comparisons between chemicals that are more or less
sensitive to this value change.

```{r new_fittables, eval = TRUE}
library(tidyverse)

# This is for new fittables where some of the values in fittable are replaced by
# HTPBTK-Consensus predictions found in level3tab$`HTPBTK-Consensus`
# Get names for fittable
fit_names <- names(fittable)
# For Vdist
fittable_Vd <- inner_join(fittable, level3tab$`HTPBTK-Consensus`,
                          by = c(
                            "DTXSID",
                            "PREFERRED_NAME" = "Compound",
                            "CAS",
                            "Species"
                          )) %>%
  mutate(Vdist = ifelse(!is.na(Vdist), Vd.pred, Vdist)) %>%
  select(all_of(fit_names))
  
# For kelim
fittable_kelim <- inner_join(fittable, level3tab$`HTPBTK-Consensus`,
                          by = c(
                            "DTXSID",
                            "PREFERRED_NAME" = "Compound",
                            "CAS",
                            "Species"
                          )) %>%
  mutate(kelim = cl.pred/Vdist) %>%
  select(all_of(fit_names))

# For Fgutabs
fittable_Fgutabs <- inner_join(fittable, level3tab$`HTPBTK-Consensus`,
                          by = c(
                            "DTXSID",
                            "PREFERRED_NAME" = "Compound",
                            "CAS",
                            "Species"
                          )) %>%
  mutate(Fgutabs = 1) %>%
  select(all_of(fit_names))


```

```{r new_fittable_stats, eval = TRUE}
this.label <- "In Vivo-HTTK_Vdist"
fit.chems <- subset(fittable_Vd, !is.na(Vdist) #| !is.na(V1)
                    )$DTXSID
out <- makeCvTpredsfromfits(
  subset(CvT.data, DTXSID %in% fit.chems),
  subset(fittable_Vd, DTXSID %in% fit.chems),
  label = this.label)

level2tab.cvt[[this.label]] <- out$cvt
level2tab.stats[[this.label]] <- out$stats
level2tab.rmsle[[this.label]] <- out$rmsle
level2tab.aafe[[this.label]] <- out$aafe
level2tab.rmsle.early[[this.label]] <- out$rmsle.early
level2tab.aafe.early[[this.label]] <- out$aafe.early
level2tab.rmsle.late[[this.label]] <- out$rmsle.late
level2tab.aafe.late[[this.label]] <- out$aafe.late
level3tab[[this.label]] <- out$level3tab

# kelim based on predicted half-life
this.label <- "In Vivo-HTTK_kelim"
fit.chems <- subset(fittable_kelim, !is.na(Vdist) #| !is.na(V1)
                    )$DTXSID
out <- makeCvTpredsfromfits(
  subset(CvT.data, DTXSID %in% fit.chems),
  subset(fittable_kelim, DTXSID %in% fit.chems),
  label = this.label)

level2tab.cvt[[this.label]] <- out$cvt
level2tab.stats[[this.label]] <- out$stats
level2tab.rmsle[[this.label]] <- out$rmsle
level2tab.aafe[[this.label]] <- out$aafe
level2tab.rmsle.early[[this.label]] <- out$rmsle.early
level2tab.aafe.early[[this.label]] <- out$aafe.early
level2tab.rmsle.late[[this.label]] <- out$rmsle.late
level2tab.aafe.late[[this.label]] <- out$aafe.late
level3tab[[this.label]] <- out$level3tab


# Fgutabs
this.label <- "In Vivo-HTTK_Fgutabs"
fit.chems <- subset(fittable_Fgutabs, !is.na(Vdist) #| !is.na(V1)
                    )$DTXSID
out <- makeCvTpredsfromfits(
  subset(CvT.data, DTXSID %in% fit.chems),
  subset(fittable_Fgutabs, DTXSID %in% fit.chems),
  label = this.label)

level2tab.cvt[[this.label]] <- out$cvt
level2tab.stats[[this.label]] <- out$stats
level2tab.rmsle[[this.label]] <- out$rmsle
level2tab.aafe[[this.label]] <- out$aafe
level2tab.rmsle.early[[this.label]] <- out$rmsle.early
level2tab.aafe.early[[this.label]] <- out$aafe.early
level2tab.rmsle.late[[this.label]] <- out$rmsle.late
level2tab.aafe.late[[this.label]] <- out$aafe.late
level3tab[[this.label]] <- out$level3tab
```

To get a better sense of this, why don't we plot it!

```{r RMSLE_plots}

lv4_df <- data.frame(
  QSPR = c(rep("HTPBTK-Consensus",
               length(unlist(level2tab.rmsle$`HTPBTK-Consensus`))),
           rep("In Vivo",
               length(unlist(level2tab.rmsle$`In Vivo Fits`))),
           rep("In Vivo-HTTK_Vdist",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist`))),
           rep("In Vivo-HTTK_Fgutabs",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs`))),
           rep("In Vivo-HTTK_kelim",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim`)))),
  DTXSID = c(names(unlist(level2tab.rmsle$`HTPBTK-Consensus`)),
             names(unlist(level2tab.rmsle$`In Vivo Fits`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim`))),
  RMSLE = c(unlist(level2tab.rmsle$`HTPBTK-Consensus`),
            unlist(level2tab.rmsle$`In Vivo Fits`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim`))
)


ggplot(data = lv4_df %>%
         mutate(QSPR = factor(QSPR, levels = c("In Vivo",
                                               "In Vivo-HTTK_Vdist",
                                               "In Vivo-HTTK_Fgutabs",
                                               "In Vivo-HTTK_kelim",
                                               "HTPBTK-Consensus"
                                               ),
                              ordered=TRUE)),
       aes(x = QSPR,
           y = RMSLE)) +
  ggbeeswarm::geom_beeswarm(size = 0.8) +
  geom_line(aes(group = DTXSID), alpha = 0.25) +
  theme_bw() +
  theme(axis.text = element_text(size = 8))

ggsave(filename = "figs/SupFig-Level4_prelim_kelimVdistFgutabs_2024July9.png",
       height = 5,
       width = 8)

ggplot(data = lv4_df %>%
         mutate(QSPR = factor(QSPR, levels = c("In Vivo",
                                               "In Vivo-HTTK_Vdist",
                                               "In Vivo-HTTK_Fgutabs",
                                               "In Vivo-HTTK_kelim",
                                               "HTPBTK-Consensus"
                                               ),
                              ordered=TRUE)),
       aes(x = QSPR,
           y = RMSLE)) +
  geom_boxplot(width = 0.5) +
  ggtitle(expression("Replacing"~italic("In Vivo")~"Estimates with QSPR-Based HTTK"))+
  scale_x_discrete(labels=c("In Vivo" = expression("All"~italic("In Vivo")),
                             "In Vivo-HTTK_Vdist"= expression(italic("In Vivo")~"+"~"V"["dist"]),
                             "In Vivo-HTTK_Fgutabs"= expression(italic("In Vivo")~"+"~"F"["bio"]),
                             "In Vivo-HTTK_kelim"= expression(italic("In Vivo")~"+"~"k"["elim"]),
                              "HTPBTK-Consensus"= "All Consensus"
                              ))+
  theme_bw() +
   theme( text  = element_text(size=16),
         axis.text.x = element_text(size=10),
         axis.text.y = element_text(size=10),
         axis.title.x = element_blank()
   )
        

ggsave(filename = "figs/Fig8-Level4_prelim_kelimVdistFgutabs_boxplot_2024July30.png",
       height = 5,
       width = 7)

ggplot(data = lv4_df %>%
         mutate(QSPR = factor(QSPR, levels = c("In Vivo",
                                               "In Vivo-HTTK_Vdist",
                                               "In Vivo-HTTK_Fgutabs",
                                               "In Vivo-HTTK_kelim",
                                               "HTPBTK-Consensus"
                                               ),
                              ordered=TRUE)),
       aes(x = QSPR,
           y = DTXSID,
           fill = RMSLE)) +
  geom_tile() +
  coord_fixed(ratio = 0.5) +
  scale_fill_viridis_c() +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 8, hjust = 1, angle = 45),
        axis.text.y = element_blank())

```

Next I want to cluster these such that they will group together based on 
the RMSLE when Fgutabs, kelim, or Vdist values from Consensus 
are substituted into the In Vivo parameters. Here I chose a k-means of 5,
which gives one cluster (4) that are greatly affected by kelim substitution,
and another cluster (5) that are fairly improved in the consensus model.

```{r clustering_analysis, eval=TRUE}
library(ComplexHeatmap)
set.seed(2024) # Want to be consistent here
# The order is fine... but it would be nice to cluster these automatically
# Need wide format for that
lv4_mat <- lv4_df %>%
  pivot_wider(names_from = QSPR,
              values_from = RMSLE) %>% 
  janitor::clean_names() %>%
  column_to_rownames(var = "dtxsid") %>%
  na.omit() %>%
  as.matrix()


ht <- ComplexHeatmap::Heatmap(lv4_mat, name = "RMSLE",
                        show_row_names = TRUE,
                        show_column_dend = FALSE,
                        row_names_gp = grid::gpar(fontsize = 6),
                        row_km = 5,
                        width = unit(1, "in"))

ComplexHeatmap::draw(ht)


ComplexHeatmap::row_order(ht) -> clustrow

png("figs/SupFig-QSARtests_heatmap_Lvl4.png",
    units = "in",
    height = 8,
    width = 8, res = 200)
ht
dev.off()

cluster_df <- lapply(clustrow, function(x) rownames(lv4_mat[x,])) %>%
  stack() %>%
  rename(DTXSID = "values", Clust = "ind")


cluster_df <- inner_join(cluster_df, fittable)

cluster_df %>%
  select(DTXSID, Clust) %>%
  inner_join(level3tab$`HTPBTK-Consensus` %>% select(-Compound)) %>%
  pivot_longer(cols = Vd.obs:cl.pred, 
               names_to = "Measurement", values_to = "Values") %>%
  ggplot(aes(x = Measurement, y = log10(Values))) +
  geom_point() +
  facet_grid(cols = vars(Clust)) +
  theme_bw() +
  theme(axis.text = element_text(hjust = 1, angle = 50))


# Read in the lists

ccd_lists <- read_csv(paste0(Sys.getenv("OD_DIR"), "Profile/",
                             "Downloads/CCD-Batch-Search_2024-07-11_02_19_19.csv" ))


ccd_lists %>%
  mutate(across(`40CFR1164`:SFEIWATER, function(x) {
    ifelse(x == "Y", 1, 0)
  })) %>%
  select(DTXSID, `40CFR1164`:SFEIWATER) -> ccd_lists

ccd_lists <- ccd_lists %>% column_to_rownames("DTXSID") %>% as.matrix()

# Get rid of those lists with no chemicals present
ccd_lists <- ccd_lists[, apply(ccd_lists, 2, sum)>0]

# Get rid of those lists with every chemical present (no cluster specificity)
ccd_lists <- ccd_lists[, apply(ccd_lists, 2, sum)<nrow(ccd_lists)]

ccd_lists <- ccd_lists[rownames(lv4_mat), ] # Reorders rows to be consistent with main heatmap


png("figs/SupFig-CCD_lists_heatmap_Lvl4.png",
    units = "in",
    height = 8,
    width = 14, res = 200)
ht_lp <- ComplexHeatmap::Heatmap(ccd_lists,
                        name = "Presence in list",
                        clustering_method_columns = "complete",
                        show_column_names = FALSE,
                        row_names_gp = grid::gpar(fontsize = 6),
                        show_row_names = TRUE,
                        col = c("grey10","green4"),
                        width = unit(4, "in"))
draw(ht_lp)

dev.off()

# Make an intermediate list of heatmaps, will add to this
ht_list <- ht+ht_lp
draw(ht_list)


chem_props <- inner_join(cluster_df %>% distinct(Clust, DTXSID),
                         chem.physical_and_invitro.data)


chem_props %>% group_by(Clust) %>%
  summarize(mean(as.numeric(Human.Clint), na.rm = TRUE),
            sd(as.numeric(Human.Clint), na.rm = TRUE))

this_list <- list()
for (i in 1:73) {
  this_list <- bind_rows(this_list, parameterize_gas_pbtk(dtxsid = pull(chem_props,
                                                      DTXSID)[i]) %>%
    as.data.frame())
}

rownames(this_list) <- pull(chem_props, DTXSID)
this_list


chem_props_scaled <- chem_props %>%
  distinct(DTXSID, logHenry, logP,
           logPwa,
           logWSol,
           MP,
           MW,
           pKa_Accept,
           pKa_Donor) %>%
  mutate(across(logHenry:pKa_Donor, as.numeric)) %>%
  column_to_rownames("DTXSID") %>%
  as.matrix()

temp_rn <- rownames(chem_props_scaled)
chem_props_scaled <- apply(chem_props_scaled, MARGIN = 2, scale)
rownames(chem_props_scaled) <- temp_rn
chem_props_scaled <- chem_props_scaled[rownames(lv4_mat), ]

ht_chemP <- Heatmap(chem_props_scaled,
                    name = "Property Z-score",
                    cluster_columns = TRUE,
                    clustering_method_columns = "single",
                    row_names_gp = grid::gpar(fontsize = 6),
                    show_row_names = TRUE,
                    width = unit(2, "in"))

ht_list <- ht + ht_lp + ht_chemP
draw(ht_list)

```

As part of the clustering analysis, I also want to do a similarity analysis.
For this I will be using python and using the SMILES data.

```{r load_smiles}
library(reticulate)
my_smiles <- read_csv(paste0(Sys.getenv("OD_DIR"), "Profile/Downloads/",
                             "CCD-Batch-Search_2024-07-16_08_42_30.csv"))


my_smiles %>% select(DTXSID, SMILES) -> my_smiles


SMILElist <- unique(my_smiles$SMILES)
use_virtualenv("r-reticulate")
mykit <- import("rdkit")

```

`rdkit` is a python library that allows us to convert SMILEs into molecular
fingerprints and then calculate Tanimoto Similarity.

```{python fingerprint_tanimoto}
import rdkit

from rdkit import Chem
from rdkit.Chem import AllChem
from rdkit import DataStructs
SMILElist = r.SMILElist
fpgen = AllChem.GetRDKitFPGenerator()
SMILElist = [Chem.MolFromSmiles(x) for x in SMILElist]
fps = [fpgen.GetFingerprint(x) for x in SMILElist]
DataStructs.TanimotoSimilarity(fps[0],fps[72])

import numpy as np
n = len(fps)
this_matrix = np.zeros((n,n))
for i in range(0,n):
  for j in range(0,n):
    this_matrix[i,j] = DataStructs.TanimotoSimilarity(fps[i],fps[j])
```


We now can take the python data structure and load it back into R to
continue to work with it.

```{r tanimoto_distance_matrix}

tani_matrix <- py_to_r(py$this_matrix)

rownames(tani_matrix) <- my_smiles$DTXSID
colnames(tani_matrix) <- my_smiles$DTXSID
tani_matrix <- tani_matrix[rownames(lv4_mat),
                           rownames(lv4_mat)]

ht3 <- Heatmap(matrix = tani_matrix,
               column_order = cluster_df$DTXSID,
               row_order = cluster_df$DTXSID,
               cluster_columns = FALSE,
               cluster_rows = FALSE,
               name = "Tanimoto distance",
               col = circlize::colorRamp2(c(0, 0.7, 1),
                                          c("grey80", 
                                            "grey40",
                                            "grey5")),
               show_row_names = TRUE,
               row_names_gp = grid::gpar(fontsize = 6),
               column_names_gp = grid::gpar(fontsize = 6),
               width = unit(5, "in"))


ComplexHeatmap::draw(ht3)

htlist <- ht + ht_lp + ht_chemP + ht3
drawn_hts <- draw(htlist)

png(filename = "figs/SupFig-Clustered_PropertyHeatmaps_Level4.png",
    height = 8,
    width = 18,
    unit = "in",
    res = 150)
drawn_hts
dev.off()



```


Next what I want to do is test how quickly the RMSLE changes. I will
start at the In Vivo value and head towards the Consensus value in 10% increments.


```{r sensitivity_analysis, eval = TRUE}
# For Vdist
fittable_Vdist <- inner_join(fittable, level3tab$`HTPBTK-Consensus`,
                          by = c(
                            "DTXSID",
                            "PREFERRED_NAME" = "Compound",
                            "CAS",
                            "Species"
                          )) %>%
  mutate(param_range = (Vd.pred - Vdist)/10,
         Vd_10p = Vdist + param_range*1,
         Vd_20p = Vdist + param_range*2,
         Vd_30p = Vdist + param_range*3,
         Vd_40p = Vdist + param_range*4,
         Vd_50p = Vdist + param_range*5,
         Vd_60p = Vdist + param_range*6,
         Vd_70p = Vdist + param_range*7,
         Vd_80p = Vdist + param_range*8,
         Vd_90p = Vdist + param_range*9,
         )

for (this_pct in seq(10, 90, by = 10)) {
  cat(paste0(this_pct, "\n"))
  this.label <- paste0("In Vivo-HTTK_Vdist", this_pct)
  this_col <- paste0("Vd_", this_pct, "p")
  this_fittable <- fittable_Vdist %>%
             mutate(Vdist = !!sym(this_col)) %>%
             select(fit_names)
  fit.chems <- subset(fittable_Vdist, !is.na(Vdist) #| !is.na(V1)
  )$DTXSID
  out <- makeCvTpredsfromfits(
    subset(CvT.data, DTXSID %in% fit.chems),
    subset(this_fittable,
           DTXSID %in% fit.chems),
    label = this.label)
  
  level2tab.cvt[[this.label]] <- out$cvt
  level2tab.stats[[this.label]] <- out$stats
  level2tab.rmsle[[this.label]] <- out$rmsle
  level2tab.aafe[[this.label]] <- out$aafe
  level2tab.rmsle.early[[this.label]] <- out$rmsle.early
  level2tab.aafe.early[[this.label]] <- out$aafe.early
  level2tab.rmsle.late[[this.label]] <- out$rmsle.late
  level2tab.aafe.late[[this.label]] <- out$aafe.late
  level3tab[[this.label]] <- out$level3tab
}


lv4_df2 <- data.frame(
  QSPR = c(rep("HTPBTK-Consensus",
               length(unlist(level2tab.rmsle$`HTPBTK-Consensus`))),
           rep("In Vivo-HTTK_Vdist10",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist10`))),
           rep("In Vivo-HTTK_Vdist20",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist20`))),
           rep("In Vivo-HTTK_Vdist30",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist30`))),
           rep("In Vivo-HTTK_Vdist40",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist40`))),
           rep("In Vivo-HTTK_Vdist50",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist50`))),
           rep("In Vivo-HTTK_Vdist60",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist60`))),
           rep("In Vivo-HTTK_Vdist70",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist70`))),
           rep("In Vivo-HTTK_Vdist80",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist80`))),
           rep("In Vivo-HTTK_Vdist90",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist90`))),
           rep("In Vivo-HTTK_Vdist",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist`))),
           rep("In Vivo",
               length(unlist(level2tab.rmsle$`In Vivo Fits`)))),
  DTXSID = c(names(unlist(level2tab.rmsle$`HTPBTK-Consensus`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist10`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist20`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist30`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist40`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist50`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist60`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist70`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist80`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist90`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist`)),
             names(unlist(level2tab.rmsle$`In Vivo Fits`))),
  RMSLE = c(unlist(level2tab.rmsle$`HTPBTK-Consensus`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist10`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist20`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist30`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist40`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist50`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist60`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist70`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist80`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist90`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Vdist`),
            unlist(level2tab.rmsle$`In Vivo Fits`))
)


ggplot(data = lv4_df2 %>%
         mutate(QSPR = factor(QSPR,
                              levels = c(
                                "HTPBTK-Consensus",
                                "In Vivo",
                                "In Vivo-HTTK_Vdist10",
                                "In Vivo-HTTK_Vdist20",
                                "In Vivo-HTTK_Vdist30",
                                "In Vivo-HTTK_Vdist40",
                                "In Vivo-HTTK_Vdist50",
                                "In Vivo-HTTK_Vdist60",
                                "In Vivo-HTTK_Vdist70",
                                "In Vivo-HTTK_Vdist80",
                                "In Vivo-HTTK_Vdist90",
                                "In Vivo-HTTK_Vdist"
                              ))),
       aes(x = QSPR,
           y = RMSLE)) +
  ggbeeswarm::geom_beeswarm(size = 0.8) +
  geom_line(aes(group = DTXSID), alpha = 0.25) +
  theme_bw() +
  theme(axis.text = element_text(size = 8, hjust = 1, angle = 40))


lv4_df2 %>%
  pivot_wider(names_from = QSPR,
              values_from = RMSLE) %>% 
  na.omit() %>%
  filter(`In Vivo` < `In Vivo-HTTK_Vdist`) %>%
  pivot_longer(cols = !DTXSID, names_to = "QSPR",
               values_to = "RMSLE") %>%
  mutate(QSPR = factor(QSPR,
                       levels = c(
                         "HTPBTK-Consensus",
                         "In Vivo",
                         "In Vivo-HTTK_Vdist10",
                         "In Vivo-HTTK_Vdist20",
                         "In Vivo-HTTK_Vdist30",
                         "In Vivo-HTTK_Vdist40",
                         "In Vivo-HTTK_Vdist50",
                         "In Vivo-HTTK_Vdist60",
                         "In Vivo-HTTK_Vdist70",
                         "In Vivo-HTTK_Vdist80",
                         "In Vivo-HTTK_Vdist90",
                         "In Vivo-HTTK_Vdist"
                       ))) %>%
  ggplot(aes(x = QSPR,
           y = RMSLE)) +
  geom_point(size = 0.8) +
  geom_line(aes(group = DTXSID), alpha = 0.25) +
  theme_bw() +
  theme(axis.text = element_text(size = 8, hjust = 1, angle = 40))


```

```{r kelim_sensitivity, eval = TRUE}
# For kelim

fittable_kelim <- inner_join(fittable, level3tab$`HTPBTK-Consensus`,
                          by = c(
                            "DTXSID",
                            "PREFERRED_NAME" = "Compound",
                            "CAS",
                            "Species"
                          )) %>%
  mutate(param_range = ((cl.pred/Vdist) - kelim)/10,
         kelim_10p = kelim + param_range*1,
         kelim_20p = kelim + param_range*2,
         kelim_30p = kelim + param_range*3,
         kelim_40p = kelim + param_range*4,
         kelim_50p = kelim + param_range*5,
         kelim_60p = kelim + param_range*6,
         kelim_70p = kelim + param_range*7,
         kelim_80p = kelim + param_range*8,
         kelim_90p = kelim + param_range*9,
         )

for (this_pct in seq(10, 90, by = 10)) {
  cat(paste0(this_pct, "\n"))
  this.label <- paste0("In Vivo-HTTK_kelim", this_pct)
  this_col <- paste0("kelim_", this_pct, "p")
  this_fittable <- fittable_kelim %>%
             mutate(kelim = !!sym(this_col)) %>%
             select(fit_names)
  fit.chems <- subset(fittable_kelim, !is.na(Vdist) #| !is.na(V1)
  )$DTXSID
  out <- makeCvTpredsfromfits(
    subset(CvT.data, DTXSID %in% fit.chems),
    subset(this_fittable,
           DTXSID %in% fit.chems),
    label = this.label)
  
  level2tab.cvt[[this.label]] <- out$cvt
  level2tab.stats[[this.label]] <- out$stats
  level2tab.rmsle[[this.label]] <- out$rmsle
  level2tab.aafe[[this.label]] <- out$aafe
  level2tab.rmsle.early[[this.label]] <- out$rmsle.early
  level2tab.aafe.early[[this.label]] <- out$aafe.early
  level2tab.rmsle.late[[this.label]] <- out$rmsle.late
  level2tab.aafe.late[[this.label]] <- out$aafe.late
  level3tab[[this.label]] <- out$level3tab
}


lv4_df3 <- data.frame(
  QSPR = c(rep("HTPBTK-Consensus",
               length(unlist(level2tab.rmsle$`HTPBTK-Consensus`))),
           rep("In Vivo-HTTK_kelim10",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim10`))),
           rep("In Vivo-HTTK_kelim20",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim20`))),
           rep("In Vivo-HTTK_kelim30",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim30`))),
           rep("In Vivo-HTTK_kelim40",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim40`))),
           rep("In Vivo-HTTK_kelim50",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim50`))),
           rep("In Vivo-HTTK_kelim60",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim60`))),
           rep("In Vivo-HTTK_kelim70",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim70`))),
           rep("In Vivo-HTTK_kelim80",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim80`))),
           rep("In Vivo-HTTK_kelim90",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim90`))),
           rep("In Vivo-HTTK_kelim",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim`))),
           rep("In Vivo",
               length(unlist(level2tab.rmsle$`In Vivo Fits`)))),
  DTXSID = c(names(unlist(level2tab.rmsle$`HTPBTK-Consensus`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim10`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim20`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim30`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim40`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim50`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim60`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim70`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim80`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim90`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_kelim`)),
             names(unlist(level2tab.rmsle$`In Vivo Fits`))),
  RMSLE = c(unlist(level2tab.rmsle$`HTPBTK-Consensus`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim10`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim20`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim30`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim40`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim50`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim60`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim70`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim80`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim90`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_kelim`),
            unlist(level2tab.rmsle$`In Vivo Fits`))
)


ggplot(data = lv4_df3 %>%
         mutate(QSPR = factor(QSPR,
                              levels = c(
                                "HTPBTK-Consensus",
                                "In Vivo",
                                "In Vivo-HTTK_kelim10",
                                "In Vivo-HTTK_kelim20",
                                "In Vivo-HTTK_kelim30",
                                "In Vivo-HTTK_kelim40",
                                "In Vivo-HTTK_kelim50",
                                "In Vivo-HTTK_kelim60",
                                "In Vivo-HTTK_kelim70",
                                "In Vivo-HTTK_kelim80",
                                "In Vivo-HTTK_kelim90",
                                "In Vivo-HTTK_kelim"
                              ))),
       aes(x = QSPR,
           y = RMSLE)) +
  ggbeeswarm::geom_beeswarm(size = 0.8) +
  geom_line(aes(group = DTXSID), alpha = 0.25) +
  theme_bw() +
  theme(axis.text = element_text(size = 8, hjust = 1, angle = 40))


lv4_df3 %>%
  pivot_wider(names_from = QSPR,
              values_from = RMSLE) %>% 
  na.omit() %>%
  filter(`In Vivo` < `In Vivo-HTTK_kelim`) %>%
  pivot_longer(cols = !DTXSID, names_to = "QSPR",
               values_to = "RMSLE") %>%
  inner_join(fittable_kelim %>% distinct(DTXSID, CAS, 
                                         Species,
                                         Reference, param_range)) %>%
  mutate(QSPR = factor(QSPR,
                       levels = c(
                         "HTPBTK-Consensus",
                         "In Vivo",
                         "In Vivo-HTTK_kelim10",
                         "In Vivo-HTTK_kelim20",
                         "In Vivo-HTTK_kelim30",
                         "In Vivo-HTTK_kelim40",
                         "In Vivo-HTTK_kelim50",
                         "In Vivo-HTTK_kelim60",
                         "In Vivo-HTTK_kelim70",
                         "In Vivo-HTTK_kelim80",
                         "In Vivo-HTTK_kelim90",
                         "In Vivo-HTTK_kelim"
                       ))) %>%
  ggplot(aes(x = QSPR,
           y = RMSLE)) +
  geom_point(mapping = aes(color = log10(param_range)), size = 0.8) +
  geom_line(aes(group = DTXSID), alpha = 0.25) +
  scale_color_viridis_c(option = "magma", end = 0.8) +
  labs(title = "kelim Sensitivity Test") +
  theme_bw() +
  theme(axis.text = element_text(size = 8, hjust = 1, angle = 40),
        plot.title = element_text(hjust = 0.5, face = "bold"))

ggsave(filename = "figs/SupFig-kelim_sensitivity_worseOff.png",
       height = 8,
       width = 8)
```


Next we do the Fgutabs sensitivity analysis. 
For this analysis, instead of making it a percent difference from the
In Vivo values, I just assume values from 0.1-0.9 at ten percent intervals, 
and the In Vivo value is somewhere in that range.
What is interesting is that there is some
chemicals where there is an improvement in RMSLE with lower _Fgutabs_
that is not the Consensus Value.

```{r Fgutabs_sensitivity}
# For Fgutabs

fittable_Fgutabs <- inner_join(fittable, level3tab$`HTPBTK-Consensus`,
                          by = c(
                            "DTXSID",
                            "PREFERRED_NAME" = "Compound",
                            "CAS",
                            "Species"
                          )) %>%
  mutate(Fgutabs_10p = 0.1,
         Fgutabs_20p = 0.2,
         Fgutabs_30p = 0.3,
         Fgutabs_40p = 0.4,
         Fgutabs_50p = 0.5,
         Fgutabs_60p = 0.6,
         Fgutabs_70p = 0.7,
         Fgutabs_80p = 0.8,
         Fgutabs_90p = 0.9,
         param_diff = 1-Fgutabs)

for (this_pct in seq(10, 90, by = 10)) {
  cat(paste0(this_pct, "\n"))
  this.label <- paste0("In Vivo-HTTK_Fgutabs", this_pct)
  this_col <- paste0("Fgutabs_", this_pct, "p")
  this_fittable <- fittable_Fgutabs %>%
             mutate(Fgutabs = !!sym(this_col)) %>%
             select(fit_names)
  fit.chems <- subset(fittable_Fgutabs, !is.na(Vdist) #| !is.na(V1)
  )$DTXSID
  out <- makeCvTpredsfromfits(
    subset(CvT.data, DTXSID %in% fit.chems),
    subset(this_fittable,
           DTXSID %in% fit.chems),
    label = this.label)
  
  level2tab.cvt[[this.label]] <- out$cvt
  level2tab.stats[[this.label]] <- out$stats
  level2tab.rmsle[[this.label]] <- out$rmsle
  level2tab.aafe[[this.label]] <- out$aafe
  level2tab.rmsle.early[[this.label]] <- out$rmsle.early
  level2tab.aafe.early[[this.label]] <- out$aafe.early
  level2tab.rmsle.late[[this.label]] <- out$rmsle.late
  level2tab.aafe.late[[this.label]] <- out$aafe.late
  level3tab[[this.label]] <- out$level3tab
}


lv4_df3 <- data.frame(
  QSPR = c(rep("HTPBTK-Consensus",
               length(unlist(level2tab.rmsle$`HTPBTK-Consensus`))),
           rep("In Vivo-HTTK_Fgutabs10",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs10`))),
           rep("In Vivo-HTTK_Fgutabs20",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs20`))),
           rep("In Vivo-HTTK_Fgutabs30",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs30`))),
           rep("In Vivo-HTTK_Fgutabs40",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs40`))),
           rep("In Vivo-HTTK_Fgutabs50",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs50`))),
           rep("In Vivo-HTTK_Fgutabs60",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs60`))),
           rep("In Vivo-HTTK_Fgutabs70",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs70`))),
           rep("In Vivo-HTTK_Fgutabs80",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs80`))),
           rep("In Vivo-HTTK_Fgutabs90",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs90`))),
           rep("In Vivo-HTTK_Fgutabs",
               length(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs`))),
           rep("In Vivo",
               length(unlist(level2tab.rmsle$`In Vivo Fits`)))),
  DTXSID = c(names(unlist(level2tab.rmsle$`HTPBTK-Consensus`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs10`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs20`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs30`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs40`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs50`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs60`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs70`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs80`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs90`)),
             names(unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs`)),
             names(unlist(level2tab.rmsle$`In Vivo Fits`))),
  RMSLE = c(unlist(level2tab.rmsle$`HTPBTK-Consensus`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs10`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs20`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs30`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs40`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs50`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs60`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs70`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs80`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs90`),
            unlist(level2tab.rmsle$`In Vivo-HTTK_Fgutabs`),
            unlist(level2tab.rmsle$`In Vivo Fits`))
)


ggplot(data = lv4_df3 %>%
         mutate(QSPR = factor(QSPR,
                              levels = c(
                                "HTPBTK-Consensus",
                                "In Vivo",
                                "In Vivo-HTTK_Fgutabs10",
                                "In Vivo-HTTK_Fgutabs20",
                                "In Vivo-HTTK_Fgutabs30",
                                "In Vivo-HTTK_Fgutabs40",
                                "In Vivo-HTTK_Fgutabs50",
                                "In Vivo-HTTK_Fgutabs60",
                                "In Vivo-HTTK_Fgutabs70",
                                "In Vivo-HTTK_Fgutabs80",
                                "In Vivo-HTTK_Fgutabs90",
                                "In Vivo-HTTK_Fgutabs"
                              ))),
       aes(x = QSPR,
           y = RMSLE)) +
  ggbeeswarm::geom_beeswarm(size = 0.8) +
  geom_line(aes(group = DTXSID), alpha = 0.25) +
  theme_bw() +
  theme(axis.text = element_text(size = 8, hjust = 1, angle = 40))


lv4_df3 %>%
  pivot_wider(names_from = QSPR,
              values_from = RMSLE) %>% 
  na.omit() %>%
  filter(`In Vivo` < `In Vivo-HTTK_Fgutabs`) %>%
  pivot_longer(cols = !DTXSID, names_to = "QSPR",
               values_to = "RMSLE") %>%
  inner_join(fittable_Fgutabs %>% distinct(DTXSID, CAS, 
                                         Species,
                                         Reference,
                                         param_diff)) %>%
  mutate(QSPR = factor(QSPR,
                       levels = c(
                         "In Vivo-HTTK_Fgutabs10",
                         "In Vivo-HTTK_Fgutabs20",
                         "In Vivo-HTTK_Fgutabs30",
                         "In Vivo-HTTK_Fgutabs40",
                         "In Vivo-HTTK_Fgutabs50",
                         "In Vivo-HTTK_Fgutabs60",
                         "In Vivo-HTTK_Fgutabs70",
                         "In Vivo-HTTK_Fgutabs80",
                         "In Vivo-HTTK_Fgutabs90",
                         "In Vivo-HTTK_Fgutabs",
                         "In Vivo",
                         "HTPBTK-Consensus"
                       ))) %>%
  ggplot(aes(x = QSPR,
           y = RMSLE)) +
  geom_point(aes(color = param_diff), size = 0.8) +
  geom_line(aes(group = DTXSID), alpha = 0.25) +
  scale_color_steps(low = "black", high = "red3") +
  labs(title = "Fgutabs Sensitivity Test") +
  theme_bw() +
  theme(axis.text = element_text(size = 8, hjust = 1, angle = 40),
        plot.title = element_text(hjust = 0.5, face = "bold"))

ggsave(filename = "figs/SupFig-fgutabs_sensitivity_worseOff.png",
       height = 8,
       width = 8)

```

This last test of reverse substitution changes _fup_ and _CLint_ to conform
to the in vivo predicted kelim.


```{r reverse_substitution}
this.label <- "HTTK-In Vivo kelim_fup"

CvT.chems.nona.kelim <- kelim_substitution(data = CvT.chems.nona,
                                           invivo = fittable,
                                           Vd_data = level3tab$`HTPBTK-Consensus`,
                                           clint_column = "Human.Clint.Max",
                                           fup_column = "Human.Fup.Mean")


out <- make_cvt_comparisons(this.label, 
                            clint.col = "Human.Clint.Max", 
                            fup.col = "invivoAdjusted.Fup",
                            CvT.data, 
                            CvT.chems.nona.kelim, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab

this.label <- "HTTK-In Vivo kelim_Clint"
out <- make_cvt_comparisons(this.label, 
                            clint.col = "invivoAdjusted.Clint", 
                            fup.col = "Human.Fup.Mean",
                            CvT.data, 
                            CvT.chems.nona.kelim, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab


level2_tab <- data.frame(
  QSPR = c(rep("HTPBTK-Consensus",
               length(unlist(level2tab.rmsle$`HTPBTK-Consensus`))),
           rep("In Vivo",
               length(unlist(level2tab.rmsle$`In Vivo Fits`))),
           rep("HTTK-In Vivo_kelim_Clint",
               length(unlist(level2tab.rmsle$`HTTK-In Vivo kelim_Clint`))),
           rep("HTTK-In Vivo_kelim_fup",
               length(unlist(level2tab.rmsle$`HTTK-In Vivo kelim_fup`)))),
  DTXSID = c(names(unlist(level2tab.rmsle$`HTPBTK-Consensus`)),
             names(unlist(level2tab.rmsle$`In Vivo Fits`)),
             names(unlist(level2tab.rmsle$`HTTK-In Vivo kelim_Clint`)),
             names(unlist(level2tab.rmsle$`HTTK-In Vivo kelim_fup`))),
  RMSLE = c(unlist(level2tab.rmsle$`HTPBTK-Consensus`),
            unlist(level2tab.rmsle$`In Vivo Fits`),
            unlist(level2tab.rmsle$`HTTK-In Vivo kelim_Clint`),
            unlist(level2tab.rmsle$`HTTK-In Vivo kelim_fup`))
)

# Which chemicals are in all 4 categories
level2_tab %>%
  pivot_wider(names_from = QSPR,
              values_from = RMSLE) %>%
  na.omit() %>%
  pull(DTXSID) -> common_ids


ggplot(level2_tab %>% filter(DTXSID %in% common_ids),
       aes(x = factor(QSPR,
                      levels = c("HTTK-In Vivo_kelim_Clint",
                                 "HTTK-In Vivo_kelim_fup",
                                 "HTPBTK-Consensus",
                                 "In Vivo")),
           y = RMSLE)) +
  ggbeeswarm::geom_beeswarm() +
  geom_line(aes(group = DTXSID),
            color = "grey40",
            alpha = 0.3) +
  labs(title = "Reverse Substition of In Vivo kelim",
       x = "QSPR") +
  theme_bw()




ggsave("figs/SupFig-revsub_invivo_kelim.png",
       height = 4,
       width = 6)


# kelim values for each cluster
cluster_df %>% 
  ggplot(aes(x = Clust, y = log2(kelim))) + 
  geom_boxplot() + theme_bw() + 
  geom_hline(yintercept = log2(26.62), linetype = "dashed") + 
  labs(title = "Elimination Constants for each cluster",
       subtitle = "(compared to median)")


ggsave("figs/SupFig-cluster_kelim.png",
       height = 5, width = 4)

```





