---
title: "TK QSPRs: Make CvT Predictions"
author: "John Wambaugh and Nisha Sipes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{QSPR Bakeoff}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we clear the memory to make sure there are no holdovers from previous R runs
```{r clear_mermor, eval=TRUE}
rm(list=ls()) 
```

To use the code in this vignette, you'll first need to load a few packages (if you haven't already).
```{r load_packages, eval = TRUE}
library(httk)
library(DescTools)
```

Load custom code 
```{r load_code, eval = TRUE}
setwd("C:/Users/jwambaug/git/tkqsars/")
source("clear_httk.R")
source("tkstats.R")
```


Set the time stamp:
```{r time_stamp, eval = TRUE}
# Time stamp:
output.prefix <- format(Sys.Date(), "%B%Y")
```

```{r load_data, eval= TRUE}
load(file="data/httkinvitro.RData")
load(file="data/Cvt-chems-level1.RData")
load(file="data/operatrainingchems.RData")
load(file="data/Cvt-data.RData")
load(file="data/fittable.RData")
```

# Level II Predictions -- CvT data
## Make Predictions

At level II we are comparing predictions made using QSPR values with actual
tissue concentration vs. time data. Most of the QSPR values are used with the
HTTK PBTK model to make predictions. I hope to get ADmet predictor PBTK
predictions too.

Level I included the predictions made with the in vitro measured values, but this 
is a subset of the total chemicals. Should probably run all statistics both
for all chemicals and just the subset to make sure that the QSPRs aren't 
affected by weird chemcials with no in vitro measured values. But I haven't 
done this yet.

Predictors evaluated:
* HTTK PBTK with in vitro measured values
* HTTK PBTK with ADmet
* HTTK PBTK with Pradeep
* HTTK PBTK with Dawson
* HTTK PBTK with OPERA
* HTTK PBTK with y-randomized in vitro measured values
* Empirical one- and two-comaprtment fits to CvT data


We load the TK stats (Level III) at this point because it makes sense to do
the Level II and III calculations are the same time (rather than rewriting 
the parameter values twice).
TK Stats (including Vd and thalf) calculated from CvTdb:

There are chemicals where the in vivo data don't permit empirical fits, drop
those from the level II/III evaluation:
```{r separate_out_badfits, eval=TRUE}
CvT.chems.nofits <- CvT.chems[
  !(CvT.chems$CASRN%in%fittable$CAS) |
  CvT.chems$CASRN %in%subset(fittable,Model=="Flat")$CAS |
  CvT.chems$CASRN %in%subset(fittable,Model=="None")$CAS
  , ]
                                

write.csv(CvT.chems.nofits[,c(
  "DTXSID",
  "PREFERRED_NAME",                               
  "CASRN")], row.names=FALSE,file="tables/SupTable-NoEmpiricalFitChems.txt")

CvT.data <- subset(CvT.data, !(CAS %in% CvT.chems.nofits$CASRN))
cat(paste(length(unique(CvT.data$DTXSID)),
          "chemicals with good invivoPKfit fits of CvT data.\n"))
cat(paste(dim(subset(fittable,!is.na(Vdist) | !is.na(V1)))[1],
          "chemicals where volume of distribution could be estimated (iv data available), allowing us to make empirical predictions.\n"))
```
## Get rid of chemical predictions that are possibly just training set lookups:
```{r remove_training_chems, eval=TRUE}
CvT.chems.notraining <- CvT.chems
for (this.qspr in unique(possible.training.chems$QSPR))
{
  this.subset <- subset(possible.training.chems, QSPR==this.qspr)
  for (this.id in this.subset$DTXSID)
  {
    CvT.chems.notraining[CvT.chems.notraining$DTXSID==this.id,
      paste("Human.Clint",this.qspr,sep=".")]<-NA
    CvT.chems.notraining[CvT.chems.notraining$DTXSID==this.id,
      paste("Human.Fup",this.qspr,sep=".")]<-NA
  }
}
length(unique(CvT.chems.notraining$DTXSID))
```

# Data size
```{r data_Size, eval=TRUE}
CvT.chems.nobad <- CvT.chems[!(CvT.chems %in% CvT.chems.nofits)] 
dim(CvT.data)
length(unique(CvT.data$DTXSID))
length(unique(CvT.chems.nobad$DTXSID))
```

```{r create_consensus_preds, eval=TRUE}
clint.cols <- colnames(CvT.chems.nobad)[
  regexpr("Clint",colnames(CvT.chems.nobad))!=-1]
CvT.chems.nobad$Human.Clint.Max<- signif(apply(
  CvT.chems.nobad[,clint.cols],1,function(x) max(x,na.rm=TRUE)), 4)
CvT.chems.nobad$Human.Clint.Mean<- signif(apply(
  CvT.chems.nobad[,clint.cols],1,function(x) mean(x,na.rm=TRUE)), 4)
logit <- function(x)
{
  return(sapply(x, function(x) log(x/(1-x))))
}
invlogit <- function(x)
{
  return(sapply(x, function(x) exp(x)/(exp(x)+1)))
}
for (this.col in c("Human.Clint.Max","Human.Clint.Mean"))
{
  CvT.chems.nobad[is.infinite(CvT.chems.nobad[,this.col]),
                  this.col] <- NA
  CvT.chems.nobad[is.nan(CvT.chems.nobad[,this.col]),
                  this.col] <- NA
}

fup.cols <- colnames(CvT.chems.nobad)[
  regexpr("Fup",colnames(CvT.chems.nobad))!=-1]
CvT.chems.nobad$Human.Fup.Mean <- apply(
  CvT.chems.nobad[,fup.cols],1,function(x) 
    signif(invlogit(mean(sapply(x, function(y) 
      logit(min(max(y,1e-8),(1-1e-8)))),na.rm=TRUE)),4))
```


## Make a version of the prediction matrix where we've replaced QSPR-chemical combinations with no predictions with the consensus predictions:
### Stop doing this -- we will assign mean RMSLE to each QSPR's output, no need to predict with mean predictions
```{r dont_remove_missing_predictions}
CvT.chems.nona <- CvT.chems.nobad
```

## Speed up run time
```{r speedup, eval=FALSE}
# Test with just five chems to make code go faster:
CvT.data <- subset(CvT.data,DTXSID %in% unique(CvT.data$DTXSID)[1:10])
CvT.chems.nona <- subset(CvT.chems.nona,DTXSID %in% CvT.data$DTXSID)
```

## Randomize the in vitro descriptors as a sort of prediction "floor"
```{r cvt_yrandomize_desc, eval = TRUE}
NUM.YRANDOM <- 10
#invitro.subset.rows <- which(!(is.na(CvT.chems.nona$Human.Clint.httk)) &
#                         !(is.na(CvT.chems.nona$Human.Fup.httk)))
# Just do yrandom for all chemicals:
invitro.subset.rows <- rep(TRUE, dim(CvT.chems.nona)[1])

# Get all chemials with measured HTTK:
reset_httk()
invitro.meas <- get_cheminfo(model="pbtk", 
                             median.only=TRUE,
                             info=c("DTXSID","Clint","Funbound.plasma"))

set.seed(123456)
for (i in 1:NUM.YRANDOM) # Ten sets of parameters
{
  yrandom.ids <- sample(1:dim(invitro.meas)[1], length(invitro.subset.rows))
  # Make sure we don't get the right values:
  accidentally.right <- yrandom.ids[invitro.meas[yrandom.ids,"DTXSID"] == 
                                      CvT.chems.nona[invitro.subset.rows,
                                                     "DTXSID"]]
  if (length(accidentally.right)== 1)
  {
    yrandom.ids[accidentally.right] <- yrandom.ids[accidentally.right] + 1
  } else {
    first.right <-accidentally.right[1]
    for (j in 1:(length(accidentally.right)-1))
    {
      yrandom.ids[accidentally.right[j]] <-
        accidentally.right[j+1]
    }
    yrandom.ids[tail(accidentally.right,1)] <-
      first.right
  }  
  CvT.chems.nona[invitro.subset.rows,
                 paste("Human.Clint.YRandom",i,sep="")] <- 
    invitro.meas[yrandom.ids, "Human.Clint"]
  CvT.chems.nona[invitro.subset.rows,
                 paste("Human.Fup.YRandom",i,sep="")] <- 
    invitro.meas[yrandom.ids, "Human.Funbound.plasma"]
}
```

# Set up function to make predictions
```{r standard_comparison_function, eval=TRUE}
level2tab.cvt <- level2tab.stats <- level2tab.rmsle <- level2tab.aafe <-
  level2tab.rmsle.early <-level2tab.aafe.early <- level2tab.rmsle.late <- 
  level2tab.aafe.late <- level3tab <- list()

make_cvt_comparisons <- function(this.label, clint.col, fup.col,
                                 CvT.data, CvT.chems.nona, fittable)
{
  clear_httk()
  chem.physical_and_invitro.data <<- add_chemtable(
    CvT.chems.nona,
    current.table=chem.physical_and_invitro.data,
    data.list=list(
      Compound="PREFERRED_NAME",
      DTXSID="DTXSID",
      CAS="CASRN",
      Funbound.plasma=fup.col,
      Clint=clint.col),
    species="Human",
    reference=this.label,
    overwrite=TRUE)
  
  print(paste("Case", this.label,
              "has sufficient parameters for",
              length(unique(c(
    get_cheminfo(model="pbtk", class.exclude=FALSE, suppress.messages=TRUE),
    get_cheminfo(model="gas_pbtk", class.exclude=FALSE, suppress.messages=TRUE)))),
              "chemicals for PBTK"))

  level2tab.list <- makeCvTpreds(CvT.data,
                                       this.label,
                                       list(Caco2.options=list(
                                         keepit100=TRUE)
                                       ))                                       

  level3tab <- maketkstatpreds(CvT.data, fittable, this.label)

  return(list(level2tab.cvt = level2tab.list$cvt,
              level2tab.stats = level2tab.list$stats,
              level2tab.rmsle = level2tab.list$rmsle,
              level2tab.aafe = level2tab.list$aafe,
              level2tab.rmsle.early = level2tab.list$rmsle.early,
              level2tab.aafe.early = level2tab.list$aafe.early,
              level2tab.rmsle.late = level2tab.list$rmsle.late,
              level2tab.aafe.late = level2tab.list$aafe.late,
              level3tab = level3tab))
}
```

Make predictions of CvT using in vitro measured data. Rather than use default
HTTK (which also pulls in things like blood to plasma ratio) we'll wipe out 
everything and then add just Clint and Fup each time:
```{r cvt_compare_invitro, eval = TRUE}
this.label <- "HTPBTK-InVitro" 
out <- make_cvt_comparisons(this.label, 
                            "Human.Clint.httk", 
                            "Human.Fup.httk",
                            CvT.data, 
                            CvT.chems.nona, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab
```

```{r cvt_compare_admet, eval = TRUE}
this.label <- "HTPBTK-ADmet" 
out <- make_cvt_comparisons(this.label, 
                            "Human.Clint.SPlus", 
                            "Human.Fup.SPlus",
                            CvT.data, 
                            CvT.chems.nona, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab
```

```{r cvt_compare_dawson, eval = TRUE}
this.label <- "HTPBTK-Dawson" 
out <- make_cvt_comparisons(this.label, 
                            "Human.Clint.Dawson", 
                            "Human.Fup.Dawson",
                            CvT.data, 
                            CvT.chems.nona, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab
```

```{r cvt_compare_pradeep, eval = TRUE}
this.label <- "HTPBTK-Pradeep" 
out <- make_cvt_comparisons(this.label, 
                            "Human.Clint.Pradeep", 
                            "Human.Fup.Pradeep",
                            CvT.data, 
                            CvT.chems.nona, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab
```

## Add OPERA predictions:
```{r cvt_compare_opera, eval = TRUE}
this.label <- "HTPBTK-OPERA"
out <- make_cvt_comparisons(this.label, 
                            "Human.Clint.OPERA", 
                            "Human.Fup.OPERA",
                            CvT.data, 
                            CvT.chems.nona, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab
```

## Add consensus predictions:
```{r cvt_compare_consensus, eval = TRUE}
this.label <- "HTPBTK-Consensus" 
out <- make_cvt_comparisons(this.label, 
                            "Human.Clint.Max", 
                            "Human.Fup.Mean",
                            CvT.data, 
                            CvT.chems.nona, 
                            fittable)
level2tab.cvt[[this.label]] <- out$level2tab.cvt
level2tab.stats[[this.label]] <- out$level2tab.stats
level2tab.rmsle[[this.label]] <- out$level2tab.rmsle
level2tab.aafe[[this.label]] <- out$level2tab.aafe
level2tab.rmsle.early[[this.label]] <- out$level2tab.rmsle.early
level2tab.aafe.early[[this.label]] <- out$level2tab.aafe.early
level2tab.rmsle.late[[this.label]] <- out$level2tab.rmsle.late
level2tab.aafe.late[[this.label]] <- out$level2tab.aafe.late
level3tab[[this.label]] <- out$level3tab
```

## Add y-random predictions:
```{r cvt_compare_yrandom, eval = TRUE}
this.label <- "HTPBTK-YRandom"
level2tab.yrandom.cvt <- list()
level2tab.yrandom.stats <- list()
level3tab.yrandom <- list()
level2tab.yrandom.rmsle <- list()
level2tab.yrandom.aafe <- list()
level2tab.yrandom.rmsle.early <- list()
level2tab.yrandom.aafe.early <- list()
level2tab.yrandom.rmsle.late <- list()
level2tab.yrandom.aafe.late <- list()
for (i in 1:NUM.YRANDOM)
{
  print(paste("Y-randomization Number",i))
  out <- make_cvt_comparisons(this.label, 
                            paste("Human.Clint.YRandom",i,sep=""), 
                            paste("Human.Fup.YRandom",i,sep=""),
                            CvT.data, 
                            CvT.chems.nona, 
                            fittable)

  level2tab.yrandom.cvt[[i]] <- out$level2tab.cvt
  level2tab.yrandom.stats[[i]] <- out$level2tab.stats
  level3tab.yrandom[[i]] <- out$level3tab
  level2tab.yrandom.rmsle[[i]] <- out$level2tab.rmsle
  level2tab.yrandom.aafe[[i]] <- out$level2tab.aafe
level2tab.yrandom.rmsle.early[[i]] <- out$level2tab.rmsle.early
level2tab.yrandom.aafe.early[[i]] <- out$level2tab.aafe.early
level2tab.yrandom.rmsle.late[[i]] <- out$level2tab.rmsle.late
level2tab.yrandom.aafe.late[[i]] <- out$level2tab.aafe.late
}
```
# Average over the ten y-random draws:
```{r cvt_average_yrandom, eval = TRUE}
this.label <- "HTPBTK-YRandom"
level2tab.cvt[[this.label]] <- level2tab.yrandom.cvt[[1]]
level2tab.stats[[this.label]] <- level2tab.yrandom.stats[[1]]
level3tab[[this.label]] <- level3tab.yrandom[[1]]
level2tab.rmsle[[this.label]] <- level2tab.yrandom.rmsle[[1]]
level2tab.aafe[[this.label]] <- level2tab.yrandom.aafe[[1]]
level2tab.rmsle.early[[this.label]] <- level2tab.yrandom.rmsle.early[[1]]
level2tab.aafe.early[[this.label]] <- level2tab.yrandom.aafe.early[[1]]
level2tab.rmsle.late[[this.label]] <- level2tab.yrandom.rmsle.late[[1]]
level2tab.aafe.late[[this.label]] <- level2tab.yrandom.aafe.late[[1]]
for (i in 2:NUM.YRANDOM)
{
  print(i)
  level2tab.cvt[[this.label]][,"Conc.pred"] <- 
    level2tab.cvt[[this.label]][,"Conc.pred"] +
    level2tab.yrandom.cvt[[i]]$Conc.pred
  level2tab.stats[[this.label]][,"Cmax.pred"] <- 
    level2tab.stats[[this.label]][,"Cmax.pred"] +
    level2tab.yrandom.stats[[i]]$Cmax.pred
  level2tab.stats[[this.label]][,"AUC.pred"] <- 
    level2tab.stats[[this.label]][,"AUC.pred"] +
    level2tab.yrandom.stats[[i]]$AUC.pred
  level3tab[[this.label]][,"Vd.pred"] <- 
    level3tab[[this.label]][,"Vd.pred"] +
    level3tab.yrandom[[i]]$Vd.pred
  level3tab[[this.label]][,"thalf.pred"] <- 
    level3tab[[this.label]][,"thalf.pred"] +
    level3tab.yrandom[[i]]$thalf.pred
  for (this.chem in names(level2tab.yrandom.rmsle[[i]]))
  {
    print(this.chem)
    level2tab.rmsle[[this.label]][[this.chem]] <-
      level2tab.rmsle[[this.label]][[this.chem]] +
      level2tab.yrandom.rmsle[[i]][[this.chem]]
    level2tab.aafe[[this.label]][[this.chem]] <-
      level2tab.aafe[[this.label]][[this.chem]] +
      level2tab.yrandom.aafe[[i]][[this.chem]]
    level2tab.rmsle.early[[this.label]][[this.chem]] <-
      level2tab.rmsle.early[[this.label]][[this.chem]] +
      level2tab.yrandom.rmsle.early[[i]][[this.chem]]
    level2tab.aafe.early[[this.label]][[this.chem]] <-
      level2tab.aafe.early[[this.label]][[this.chem]] +
      level2tab.yrandom.aafe.early[[i]][[this.chem]]
    level2tab.rmsle.late[[this.label]][[this.chem]] <-
      level2tab.rmsle.late[[this.label]][[this.chem]] +
      level2tab.yrandom.rmsle.late[[i]][[this.chem]]
    level2tab.aafe.late[[this.label]][[this.chem]] <-
      level2tab.aafe.late[[this.label]][[this.chem]] +
      level2tab.yrandom.aafe.late[[i]][[this.chem]]
  }
}
level2tab.cvt[[this.label]][,"Conc.pred"] <- 
      signif(level2tab.cvt[[this.label]][,"Conc.pred"]/NUM.YRANDOM,
             4)
level2tab.stats[[this.label]][,"Cmax.pred"] <- 
      signif(level2tab.stats[[this.label]][,"Cmax.pred"]/NUM.YRANDOM,
             4)
level2tab.stats[[this.label]][,"AUC.pred"] <- 
      signif(level2tab.stats[[this.label]][,"AUC.pred"]/NUM.YRANDOM,
             4)
for (this.chem in names(level2tab.rmsle[[this.label]]))
{
  level2tab.rmsle[[this.label]][[this.chem]] <-
    signif(level2tab.rmsle[[this.label]][[this.chem]]/NUM.YRANDOM,
           4)
  level2tab.aafe[[this.label]][[this.chem]] <-
    signif(level2tab.aafe[[this.label]][[this.chem]]/NUM.YRANDOM,
           4)
  level2tab.rmsle.early[[this.label]][[this.chem]] <-
    signif(level2tab.rmsle.early[[this.label]][[this.chem]]/NUM.YRANDOM,
           4)
  level2tab.aafe.early[[this.label]][[this.chem]] <-
    signif(level2tab.aafe.early[[this.label]][[this.chem]]/NUM.YRANDOM,
           4)
    level2tab.rmsle.late[[this.label]][[this.chem]] <-
    signif(level2tab.rmsle.late[[this.label]][[this.chem]]/NUM.YRANDOM,
           4)
  level2tab.aafe.late[[this.label]][[this.chem]] <-
    signif(level2tab.aafe.late[[this.label]][[this.chem]]/NUM.YRANDOM,
           4)
}
```

The performance of actual 1 compartment model fits provides an upper limit
of how good we can get (thanks Rusty)
```{r cvt_compare_fits, eval = TRUE}
this.label <- "In Vivo Fits"
fit.chems <- subset(fittable, !is.na(Vdist) | !is.na(V1))$DTXSID
out <- makeCvTpredsfromfits(
  subset(CvT.data, DTXSID %in% fit.chems),
  subset(fittable, DTXSID %in% fit.chems),
  label = this.label)

level2tab.cvt[[this.label]] <- out$cvt
level2tab.stats[[this.label]] <- out$stats
level2tab.rmsle[[this.label]] <- out$rmsle
level2tab.aafe[[this.label]] <- out$aafe
level2tab.rmsle.early[[this.label]] <- out$rmsle.early
level2tab.aafe.early[[this.label]] <- out$aafe.early
level2tab.rmsle.late[[this.label]] <- out$rmsle.late
level2tab.aafe.late[[this.label]] <- out$aafe.late
level3tab[[this.label]] <- out$level3tab
```


```{r save_level2_tables, eval = TRUE}
save(
  level2tab.cvt,
  level2tab.stats,
  level2tab.rmsle,
  level2tab.aafe,
  level2tab.rmsle.early,
  level2tab.aafe.early,
  level2tab.rmsle.late,
  level2tab.aafe.late,
  file="data/level2-tables.RData")
save(
  level2tab.yrandom.cvt,
  level2tab.yrandom.stats,
  level3tab.yrandom,
  level2tab.yrandom.rmsle,
  level2tab.yrandom.aafe,
  level2tab.yrandom.rmsle.early,
  level2tab.yrandom.aafe.early,
  level2tab.yrandom.rmsle.late,
  level2tab.yrandom.aafe.late,
  file = "data/level2-yrandomindividualresults.RData")
save(
  level3tab,
     file="data/level3-tables.RData")
save(CvT.chems.nona, file="data/cvT-chems-nona.RData")
```
